---
title: "Randomized Controlled Trials"
---

> ### **`Assignment 8:`**  
Given a set of Data about a randomized experiment run by an online shop. E-commerce websites frequently conduct numerous randomized experiments, commonly referred to as AB testing in a business context.

1. Check whether the covariates are balanced across the groups. Use a plot to show it.  
2. Run a regression to find the effect of chatbot on sales.  
3. Find subgroup-specific effects by including an interaction. Compute a CATE for one exemplary group.  
4. Use the outcome variable purchase and run a logistic regression and interpret the coefficient for chatbot.  

### **Solution:**  

1. Differences Plots: to check the balance of the covariates, their differences are plotted for both groups (with/ without chatbot).

```{r}
#Load Library & data:

library(tidyverse)


abtest_online <- readRDS("D:/OneDrive/Samantha/TUHH/1stsemester/Causal Data Science for Business Analytics (SE)/Causal_Data_Science_Data/abtest_online.rds")

head(abtest_online)

#Previous Visits difference plot:
compare_previsit <- 
  ggplot(abtest_online, 
         aes(x = chatbot, 
             y = previous_visit, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "Previous Visit", title = "Difference in previous visits")

compare_previsit

#Mobile Device users difference plot:
compare_mobiledevice <- 
  ggplot(abtest_online, 
         aes(x = chatbot, 
             y = mobile_device, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "Mobile Device", title = "Difference in mobile users")

compare_mobiledevice

#Purchase difference plot:
compare_purchase <- 
  ggplot(abtest_online, 
         aes(x = chatbot, 
             y = purchase, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "Purchase", title = "Difference in purchases")

compare_purchase

#Purchases amount difference plot:
compare_purchaseamount <- 
  ggplot(abtest_online, 
         aes(x = chatbot, 
             y = purchase_amount, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "Purchase Amount", title = "Difference in purchases amount")

compare_purchaseamount
```

As illustrated by the plots the covariates are not balanced.

2. The effect of chatbot on sales:

```{r}
#Linear Regression on Chatbot:
lm_chatbot <- lm(purchase_amount ~ chatbot, data=abtest_online)
summary(lm_chatbot)
```

By checking the estimate value, having a chatbot has a negative relation with the purchases amount (sales).

3. Mobile users sub-group effect:

```{r}
#Linear Regression on Chatbot in interaction with mobile users:
lm_chatbot_mobusr <- lm(purchase_amount ~ chatbot* mobile_device, data=abtest_online)
summary(lm_chatbot_mobusr)
```

Negative estimate value indicates negative relation.

4. Logistic regression of purchase on chatbot: 

```{r}
logistic_regression <- glm(purchase ~ chatbot, family=binomial(link='logit'), abtest_online)
summary(logistic_regression)
```

The estimate value for ChatbotTrue is negative which means that having a chatbot decreases the chances of purchasing from a user and the p-value is less than 0.5 meaning this has a statistically significant effect. $\beta = -0.98939$ then $e^\beta = e^{-0.98939} = 0.372$ and this means having a chatbot is associated with a $62.8\% (1-0.372=0.628)$ reduction in the purchase possibility.  